Last glacial cycle glacier erosion potential in the Alps

### 2020-12-24 articles/erosion/alps-erosion.tex
Add figures and captions in erosion manuscript.

%\usepackage{doi}
\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%\usepackage[pdftex]{xcolor}
%\usepackage[pdftex]{graphicx}
%\usepackage[authoryear,round]{natbib}

@@

%\graphicspath{{../../figures/}}

@@

    Fig.~\ref{fig:landscape} -- Alpine glacial erosion landscape photos.
        (a) piedmont overdeepening (ca. 100 km), Lake Geneva
        (b) glacial valley (ca. 10 km), Lauterbrunnen
        (c) mountain cirque (ca. 1 km), Chüebodengletscher

@@

    Fig.~\ref{fig:transects} -- Erosion rate along transects.
    Fig.~\ref{fig:evolution} -- Erosion rate and ice volume.
    Fig.~\ref{fig:hypsogram} -- Erosion rate and elevation.

@@

%\bibliographystyle{frontiersinSCNS_ENG_HUMS}
%\bibliography{../../references/references}

% ----------------------------------------------------------------------
% Figures
%\clearpage
% ----------------------------------------------------------------------

%    \begin{figure}
%      \centerline{\includegraphics{alpero_cumulative}}
%      \caption{%
%          Modelled glacial erosion over the last glacial cycle.}
%      \label{fig:glerosion}
%    \end{figure}

>>>>

%\usepackage{doi}
\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear,round]{natbib}

@@

% custom colours
\definecolor{darkblue}{cmyk}{0.9,0.3,0.0,0.0}
\definecolor{darkgreen}{cmyk}{0.8,0.0,1.0,0.0}
\definecolor{darkred}{cmyk}{0.1,0.9,0.8,0.0}
\definecolor{darkorange}{cmyk}{0.0,0.5,1.0,0.0}
\definecolor{darkpurple}{cmyk}{0.6,0.7,0.0,0.0}
\definecolor{darkbrown}{cmyk}{0.23,0.73,0.98,0.12}

% custom commands
\newcommand{\idea}[1]{\textcolor{darkgreen}{\emph{[\textbf{IDEA:} #1]}}}
\newcommand{\note}[1]{\textcolor{darkblue}{\emph{[\textbf{NOTE:} #1]}}}
\newcommand{\todo}[1]{\textcolor{darkred}{\emph{[\textbf{TODO:} #1]}}}
\newcommand{\aref}[0]{\textcolor{darkblue}{\textbf{[REF.]}}}

\graphicspath{{../../figures/}}

@@

    Fig.~\ref{fig:landscape} -- Alpine glacial erosion landscape photos.

@@

    Fig.~\ref{fig:transects} -- Erosion rate along transects.

    Fig.~\ref{fig:evolution} -- Erosion rate and ice volume.

    Fig.~\ref{fig:hypsogram} -- Erosion rate and elevation.

@@

\bibliographystyle{abbrvnat}
\bibliography{../../../references/references}

% ----------------------------------------------------------------------
% Figures
\clearpage
% ----------------------------------------------------------------------

    \begin{figure*}
      \centerline{\includegraphics{alpero_landscape}}
      \caption{%
        Alpine glacial erosion landscape diversity.
        \textbf{(a)} Piedmont overdeepening of Lake Constance, ca.~10x50\,km.
        \textbf{(b)} Glacial trough of Lauterbrunnental, ca.~1x10\,km.
        \textbf{(c)} Mountain cirque of Chüebodengletscher, ca.~1x1\,km.}
      \label{fig:landscape}
    \end{figure*}

    \begin{figure*}
      \centerline{\includegraphics{alpero_cumulative}}
      \caption{%
        \textbf{(a)} Modelled cumulative (time-integrated) glacial erosion
          potential over the last glacial cycle.
        \textbf{(b)} Modelled total ice volume in centimetres of sea-level
          equivalent (cm~s.l.e., black), volumic (domain-integrated) erosion
          rate (light brown) and 100-a running mean (dark brown). Shaded gray
          areas indicate the timing for MIS~2 and~4
          \citep{Lisiecki.Raymo.2005}.} \label{fig:cumulative}
    \end{figure*}

    \begin{figure}
      \centerline{\includegraphics{alpero_evolution}}
      \caption{%
        Modelled volumic (domain-integrated) erosion rate (light brown) and 100-a
        running mean (dark brown) in relation to modelled total ice volume in
        centimetres of sea-level equivalent (black).}
      \label{fig:evolution}
    \end{figure}

    \begin{figure*}
      \centerline{\includegraphics{alpero_transects}}
      \caption{%
        \textbf{(a, b, c)} Modelled instantaneous erosion rate of the Rhine
          Glacier for selected post-Last Glacial Maximum ages.
        \textbf{(d)} Interpolated instantaneous erosion rate along a Rhine
          Glacier transect for the entire last glacial cycle (upper panels
          dashed line).}
      \label{fig:transects}
    \end{figure*}

    \begin{figure*}
      \centerline{\includegraphics{alpero_hypsogram}}
      \caption{%
        \textbf{(a)} Modelled erosion rate ``hypsogram'', showing the geometric
          mean of (non-zero) modelled erosion rates in 10-m elevation bands
          across the entire model domain and its time evolution.
        \textbf{(b)} Same as Fig.~\ref{fig:cumulative}b.}
      \label{fig:hypsogram}
    \end{figure*}

    \begin{figure*}
      \centerline{\includegraphics{alpero_sensitivity}}
      \caption{%
        Modelled cumulative glacial erosion potential over the last glacial
        cycle without \textbf{(a, b, c)} and with \textbf{(d, e, f)}
        paleo-precipitation corrections, and using three different
        palaeo-temperature histories \citep[see][]{Seguinot.etal.2018}.}
      \label{fig:sensitivity}
    \end{figure*}

    \begin{figure*}
      \centerline{\includegraphics{alpero_uncertainty}}
      \caption{%
        Modelled cumulative (time-integrated) glacial erosion potential for
        three different erosion laws published by
        \textbf{(a)} \citet{Cook.etal.2020},
          $1.665 \times 10^{-1} \textbf{u}_\mathrm{b} ^{0.6459}$,
        \textbf{(b)} \citet{Herman.etal.2015},
          $2.7 \times 10^{-7} \textbf{u}_\mathrm{b} ^{2.02}$
          (same as Fig.~\ref{fig:cumulative}a), amd
        \textbf{(c)} \citet{Koppes.etal.2015},
          $5.2 \times 10^{-8} \textbf{u}_\mathrm{b} ^{2.34}$.
        \textbf{(d)} Corresponding erosion power laws, and
        \textbf{(e)} modelled cumulative (time-integrated) glacial erosion
          potential along a Rhine Glacier transect (upper panels dashed line).}
      \label{fig:uncertainty}
    \end{figure*}
